Figure: the scatterblob

### 2022-03-25 R/roles_table.Rmd
rename and edit so .Rmd generated table stands alone kindof

---
knit: (function(input_file, encoding) {
  out_dir <- '../content';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '09.figures-tables.md'))})
output: 
  md_document:
    variant: gfm #for debugging, forces table to be markdown, not html
    # variant: markdown
---

@@

## Tables

@@

## Figures

Alternate way:

![Caption for the example figure.](../content/images/figure-2.png){#fig:testfig}

test citation for figure @fig:testfig

>>>>

---
knit: (function(input_file, encoding) {
  out_dir <- '../content';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '10.roles_table.md'))})
output: 
  md_document:
    variant: gfm #for debugging, forces table to be markdown, not html
    # variant: markdown
---

@@

<!--DO NOT EDIT. Generated from R/roles_table.Rmd, so edit that and render it to make changes.  This should get tacked on to the end of 09.figures-tables.md when compiled by Manubot -->

@@
